Draft

### 2020-08-10 Draft.Rmd
change the line space, fontsize, and margins to thesis requirement.

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes: \usepackage{amsmath}
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
---

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered") %>% 
  add_header_above(c("Table 7: Descriptive statistics"=9))
```

@@

```{r}
sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11765)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered")%>% 
  add_header_above(c("Table 13: Descriptive statistics"=9))
```

>>>>

---
compact-title: no
editor_options:
  chunk_output_type: console
  header-includes: 
  - \usepackage{amsmath}
  - \usepackage{setspace}\doublespacing
geometry: margin=1in
fontsize: 12pt
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4.5
---

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered",font_size = 10) %>% 
  add_header_above(c("Table 7: Descriptive statistics"=9))
```

@@

```{r}
sum <- data.frame(Series="Log(VIX)",Min = as.numeric(summary[1]), Median = as.numeric(summary[3]), Mean = as.numeric(summary[4]), Max = as.numeric(summary[6]),Skewness= vixsk,Kurtosis=vixkt,JB.Test=410.77,LB.Test=11765)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered",font_size = 10)%>% 
  add_header_above(c("Table 13: Descriptive statistics"=9))
```
